\providecommand{\algname}{optim\_mlp-model-opt\_ev\_25\_20{}}
\providecommand{\algfolder}{}
\providecommand{\bbobpptablecaption}[1]{
%
    Expected running time (ERT in number of function 
    evaluations) divided by the best ERT measured during BBOB-2009. The ERT 
    and in braces, as dispersion measure, the half difference between 90 and 
    10\%-tile of bootstrapped run lengths appear in the second row of each cell,  
    the best ERT
    %
    in the first. The different target \Df-values are shown in the top row. 
    \#succ is the number of trials that reached the (final) target $\fopt + 10^{-8}$.
    %
    The median number of conducted function evaluations is additionally given in 
    \textit{italics}, if the target in the last column was never reached. 
    \textbf{Bold} entries are statistically significantly better (according to
    the rank-sum test) compared to the best algorithm in BBOB-2009, with
    $p = 0.05$ or $p = 10^{-k}$ when the number $k > 1$ is following the
    $\downarrow$ symbol, with Bonferroni correction by the number of
    functions.
    
}
\providecommand{\bbobppfigdimlegend}[1]{
%
    Expected number of $f$-evaluations (\ERT, lines) to reach $\fopt+\Df$;
    median number of $f$-evaluations (+) to reach the most difficult
    target that was reached not always but at least once; maximum number of
    $f$-evaluations in any trial ({\color{red}$\times$}); interquartile 
    range with median (notched boxes) of simulated runlengths
    to reach $\fopt+\Df$; all values are divided by dimension and plotted as 
    $\log_{10}$ values versus dimension. %
    %
    Shown are $\Df = 10^{\{1, 0, -1, -2, -3, -5, -8\}}$.  
    Numbers above \ERT-symbols (if appearing) indicate the number of trials reaching the respective target. 
    The light thick line with diamonds indicates the respective best result from BBOB-2009 for $\Df=10^{-8}$. 
    Horizontal lines mean linear scaling, slanted grid lines depict quadratic scaling.  
    
}
\providecommand{\bbobpprldistrlegend}[1]{
%
     Empirical cumulative distribution functions (ECDF), plotting the fraction of 
     trials with an outcome not larger than the respective value on the $x$-axis. 
     #1%
     Left subplots: ECDF of the number of function evaluations (FEvals) divided by search space dimension $D$, 
     to fall below $\fopt+\Df$ with $\Df=10^{k}$, where $k$ is the first value in the legend. 
     The thick red line represents the most difficult target value $\fopt+10^{-8}$. %
     Legends indicate for each target the number of functions that were solved in at
     least one trial within the displayed budget.
     %
     Right subplots: ECDF of the 
     best achieved $\Df$ 
     for running times of $0.5D, 1.2D, 3D, 10D, 100D, 1000D,\dots$
     function evaluations 
     (from right to left cycling cyan-magenta-black\dots) and final $\Df$-value (red), 
     where \Df\ and \textsf{Df} denote the difference to the optimal function value. 
     Light brown lines in the background show ECDFs for the most difficult target of all 
     algorithms benchmarked during BBOB-2009.
     
}
\providecommand{\bbobloglossfigurecaption}[1]{
%
    \ERT\ loss ratios (see Figure~\ref{tab:ERTloss} for details).  
    Each cross ({\color{blue}$+$}) represents a single function, the line is the geometric mean.
    
}
\providecommand{\bbobloglosstablecaption}[1]{
% \bbobloglosstablecaption{}
    \ERT\ loss ratio versus the budget (both in number of $f$-evaluations
    divided by dimension). The target value \ftarget\ for a given budget
    \FEvals\ is the best target $f$-value reached within the budget by the given
    algorithm. Shown is the \ERT\ of the given algorithm divided by best \ERT\
    seen in GECCO-BBOB-2009 for the target \ftarget, or, if the best algorithm
    reached a better target within the budget, the budget divided by the best
    \ERT. Line: geometric mean. Box-Whisker error bar: 25-75\%-ile with median
    (box), 10-90\%-ile (caps), and minimum and maximum \ERT\ loss ratio
    (points). The vertical line gives the maximal number of function evaluations
    in a single trial in this function subset. See also
    Figure~\ref{fig:ERTlogloss} for results on each function subgroup.
    
}
